---
title: "HW_11_DS775"
author: "Jarrod Pelkofer"
date: "April 2, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 20.1-3e
```{r}

sales <- c(rep(2,4), rep(3,7), rep(4,8), rep(5,5), 6)
set.seed(44)
sales_sim <- sample(sales, 300, replace = TRUE)
mean_sim <- mean(sales_sim)
mean_sim

```

e) The 300 day simulation resulted in an average of 3.613 stoves per day, .067 stoves/day less than the 25 day average.

## 20.6-6
```{r}
simulations <- 1000

purchasePrice <- 1.50
salesPrice <- 2.50
refundPrice <- 0.50

copiesOrdered <- c(50:60)

for(i in 1:length(copiesOrdered)){
  set.seed(101)
  copiesSold <- sample(40:70, simulations, replace = TRUE)
  SalesRevenue <- salesPrice*pmin(copiesOrdered[i],copiesSold)
  PurchasingCost <- purchasePrice*copiesOrdered[i]
  Refund <- refundPrice*pmax(copiesOrdered[i]-copiesSold,0)
  Profit <- SalesRevenue-PurchasingCost+Refund
  avgProfit <- mean(Profit)
  print(paste("Order Quantity:", copiesOrdered[i], "Mean:", avgProfit))
}
```
The average profit it highest at an order quantity of 54.

##HW 20.6-7
```{r}
set.seed(333)
Stocks_year0 <- 5000 * (1 + rnorm(1000, .08, .06))
Stocks_year1 <- (2000 + Stocks_year0) * (1 + rnorm(1000, .08, .06))
Stocks_year2 <- (2000 + Stocks_year1) * (1 + rnorm(1000, .08, .06))
Stocks_year3 <- (2000 + Stocks_year2) * (1 + rnorm(1000, .08, .06))
Stocks_year4 <- (2000 + Stocks_year3) * (1 + rnorm(1000, .08, .06))

Bonds_year0 <- 5000 * (1 + rnorm(1000, .04, .03))
Bonds_year1 <- (2000 + Bonds_year0) * (1 + rnorm(1000, .04, .03))
Bonds_year2 <- (2000 + Bonds_year1) * (1 + rnorm(1000, .04, .03))
Bonds_year3 <- (2000 + Bonds_year2) * (1 + rnorm(1000, .04, .03))
Bonds_year4 <- (2000 + Bonds_year3) * (1 + rnorm(1000, .04, .03))

Savings_year5 <- 4000

College_Fund <- Stocks_year4 + Bonds_year4 + Savings_year5

#a)
avg_College_Fund <- mean(College_Fund)
avg_College_Fund
#b)
sd_College_Fund <- sd(College_Fund)
sd_College_Fund
#c)
prob_35K <- sum(College_Fund >=35000)/length(College_Fund)
prob_35K
#d)
prob_40K <- sum(College_Fund >=40000)/length(College_Fund)
prob_40K
```
a) AVerage college fund at the end of year 5 would be $36,076.34.
b) The standard deviation of the college fund at the end of year 5 would be $1,848.54.
c) There is a probability of 71.5% that the college fund will be at least $35,000.
d) There is a probability of 1.9% that the college fund will be at least $40,000.

##HW 20.6-9
```{r, message=FALSE, warning=FALSE}
library(triangle)
library(tidyverse)

#a)
project_cost <- 5
bid_cost <- .05
RPI_Bid <- 5.7
RPI_Total_Cost <- bid_cost + project_cost
RPI_Profit <- RPI_Bid - RPI_Total_Cost

set.seed(99)
competitor_1 <- rtriangle(1000, a = (project_cost*1.05), b = (project_cost*1.40), c = (project_cost*1.20))
competitor_2 <- rtriangle(1000, a = (project_cost*1.05), b = (project_cost*1.40), c = (project_cost*1.20))
competitor_3 <- rtriangle(1000, a = (project_cost*1.05), b = (project_cost*1.40), c = (project_cost*1.20))
competitor_4 <- rtriangle(1000, a = (project_cost*1.05), b = (project_cost*1.40), c = (project_cost*1.20))

RPI_Bids <- rep(RPI_Bid, 1000)
min_bid <- pmin(RPI_Bids, competitor_1, competitor_2, competitor_3, competitor_4)
prob_RPI_WIN <- sum(min_bid==RPI_Bid)/length(min_bid)

profit <-  double()
for(b in 1:length(min_bid)){
  if(min_bid[b] == RPI_Bid){
    profit <- c(profit, RPI_Profit)
  }else{
    profit <- c(profit, -.05)
  }
}

avg_profit <- mean(profit)


#b)
RPI_Bid <- seq(5.3,6.0, .1)
avg_profits <- double()
st_devs <- double()
for(b in 1:length(RPI_Bid)){
  profit <-  double()
  RPI_Bids <- rep(RPI_Bid[b], 1000)
  min_bid <- pmin(RPI_Bids, competitor_1, competitor_2, competitor_3, competitor_4)
  for(m in 1:length(min_bid)){
    if(min_bid[m] == RPI_Bid[b]){
      gain <- RPI_Bid[b] - RPI_Total_Cost
      profit <- c(profit, gain)
    }else{
      profit <- c(profit, -.05)
    }
  }
  st_devs <- c(st_devs, sd(profit))
  avg_profits <- c(avg_profits, mean(profit))
}  

parameter_report <- data.frame(RPI_Bid, avg_profits, st_devs)
parameter_report

#c)
ggplot(parameter_report, aes(RPI_Bid, avg_profits)) +
  geom_line() +
  geom_point() + 
  geom_ribbon(aes(ymin=avg_profits-st_devs, ymax=avg_profits+st_devs, x=RPI_Bid, fill = "band"), alpha = .3) + 
  scale_fill_manual("", values = 'grey12') + 
  labs(title = "Simulated Avg Profit", y = "Avg Profit (In Millions)", x = "RPI Bid (In Millions)") +
  theme(legend.position = "none")

#d) 

RPI_Bid <- seq(5.3,6.0, .01)
avg_profits <- double()
st_devs <- double()
for(b in 1:length(RPI_Bid)){
  profit <-  double()
  RPI_Bids <- rep(RPI_Bid[b], 10000)
  min_bid <- pmin(RPI_Bids, competitor_1, competitor_2, competitor_3, competitor_4)
  for(m in 1:length(min_bid)){
    if(min_bid[m] == RPI_Bid[b]){
      gain <- RPI_Bid[b] - RPI_Total_Cost
      profit <- c(profit, gain)
    }else{
      profit <- c(profit, -.05)
    }
  }
  avg_profits <- c(avg_profits, mean(profit))
}

bid_profits <- data.frame(RPI_Bid, avg_profits)
bid_profits %>% filter(avg_profits==max(avg_profits))
```

a) The probability that RPI will win the bid is 52.1%. The average profit would be $314,700.
b) A bid of $5.5 million maximizes RPI's average profit.
d) Looking at 71 bid amounts and running 10,000 simulations on each, a bid of $5.53 million maximized the mean profit (368,170). 

## HW 28.3
a) Uniform distribution with parameters(302, 496)
b) Max Extreme distribution with parameters(363.9972, 46.4134)


## HW 28.4
```{r}
#a)
sims <- 1000
set.seed(333)
funding <- rnorm(sims, 6, 1)
design <- runif(sims, 6, 10)
site_prep <- rtriangle(sims, 1.5, 2.5, 2)
foundation <- rtriangle(sims, 1.5, 3, 2)
framing <- rtriangle(sims, 3,6,4)
electric <- rtriangle(sims, 2,5,3)
plumbing <- rtriangle(sims, 3,5,4)
walls_roof <- rtriangle(sims, 4,7,5)
finish_work <- rtriangle(sims, 5,7,6)
landscape <- rep(5, 1000)

completion_times <- funding+design+site_prep+foundation+framing+electric+plumbing+walls_roof+finish_work+landscape
avg_completion_time <- mean(completion_times)
avg_completion_time

#b) 
thirty_six <- sum(completion_times <= 36)/length(completion_times)
thirty_six

#c) 
tasks <- data.frame(funding, design, site_prep, foundation, framing, electric, plumbing, walls_roof, finish_work, landscape, completion_times)
sensitivity <- as.data.frame(t(cor(tasks$completion_times, tasks)))
sensitivity <- sensitivity %>% rename(cor = V1)
task <- c('funding', 'design', 'site_prep', 'foundation', 'framing', 'electric', 'plumbing', 'walls_roof', 'finish_work', 'landscape', 'completion_times')
sensitivity <- data.frame(task, sensitivity$cor)
sensitivity <- sensitivity %>% rename(cor = sensitivity.cor)
ggplot(sensitivity %>% drop_na() %>% filter(cor < 1), aes(fct_reorder(task, cor), cor)) +
         geom_bar(stat = 'identity') +
         coord_flip() +
         labs(title = 'Sensitivity Chart', x='Task')
```

a) The average completion time of the project is 46.26 months over 1000 simulations.
b) 
c)

##28.10
```{r}
#a)
available_seats <- 150
operating_cost <- -30000
ticket_price <- 300
bump_cost <- -450

reservations_accepted <- c(180:190)
sim_Size <- 1000 
set.seed(1000)
demand <- rnorm(sim_Size, 195, 30)

avg_profit <- double()
sd_profit <- double()
for(i in 1:length(reservations_accepted)){
  actual <- rbinom(sim_Size, reservations_accepted[i], .80)
  
  filled_seats <- pmin(available_seats, actual)
  avg_filled_seats <- mean(filled_seats)
  
  denied <- pmax(0, actual-available_seats)
  avg_denied <- mean(denied)
  
  profit <- operating_cost + (filled_seats*ticket_price) + (denied*bump_cost)
  avg_profit <- c(avg_profit, mean(profit))
  sd_profit <- c(sd_profit, sd(profit))
}

parameter_report <- data.frame(reservations_accepted, avg_profit, sd_profit)
parameter_report

#b)
ggplot(parameter_report, aes(reservations_accepted, avg_profit)) +
  geom_line() +
  geom_point() +
  geom_ribbon(aes(ymin=avg_profit-sd_profit, ymax=avg_profit+sd_profit, x=reservations_accepted, fill = "band"), alpha = .3) + 
  scale_fill_manual("", values = 'grey12') +
  scale_x_continuous(breaks = c(180:190)) + 
  theme(legend.position = "none")

#c)
reservations_accepted <- c(150:200)
sim_Size <- 1000 
set.seed(1000)
demand <- rnorm(sim_Size, 195, 30)

avg_profit <- double()
sd_profit <- double()
for(i in 1:length(reservations_accepted)){
  actual <- rbinom(sim_Size, reservations_accepted[i], .80)
  
  filled_seats <- pmin(available_seats, actual)
  avg_filled_seats <- mean(filled_seats)
  
  denied <- pmax(0, actual-available_seats)
  avg_denied <- mean(denied)
  
  profit <- operating_cost + (filled_seats*ticket_price) + (denied*bump_cost)
  avg_profit <- c(avg_profit, mean(profit))
  sd_profit <- c(sd_profit, sd(profit))
}

reservations <- data.frame(reservations_accepted, avg_profit)
best <- reservations %>% filter(avg_profit == max(avg_profit))
best


```

a) Over 1000 simiulations, accepting 185 reservations yielded the highest average profit (13,444.95). Accepting 180 reservations yielded the lowest average profit (12979.80).
c) Over 1000 simiulations, accepting 185 reservations yielded the highest average profit (13,466.25).
